Supplementary Material for \\Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2021-08-31 paper/ifo-supplementary-material.tex
adding teaching references and paragrph in sup mat

>>>>

The experimental apparatus presented here provides an opportunity to bring together physics and electrical engineering topics in the lab environment. 
Several examples of cross-disciplinary teaching can be found in the literature, for example see Refs.~\cite{OConnerSibrayForinash:2001, PiersonGurlandCrawford:2002, CafarelliEtAl:2012, MakanKopaszGingl:2014}. 
Cross-disciplinary experimental projects between physics and engineering students can increase student understanding of overlapping concepts through contextual learning and also improve student motivation~\cite{PiersonGurlandCrawford:2002}. 
Realistic and open-ended projects spanning both topics allow students a better understanding of real-world application of these topics and of the dependency between scientists and engineers (as shown by the collaborative project presented in Ref.~\cite{OConnerSibrayForinash:2001}).
The optical microphone presented here can similarly be used as a teaching tool for students to conduct investigations into signal processing techniques with a physical system.
